Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-13 docs/thesis/chap-cern_math_explorer.tex
minor fixes to the document: distributed system(s) latex_editor (that)
Syntax and grammar fixes

\section{Features Extraction}
Our main goal is to develop a system that compliments the already available search capabilities in Invenio and in particular the CDS instance. Our system was developed on top of the  the Apache Solr/Lucene framework. CDS already uses Solr as a search engine layer, so developing $5e^{x+y}$(CDS) using this technology supposed a reasonable choice. One of the main steps while building an IR tool, is understanding the data and what kind of features can be extracted from it: If the system is based on text, then tasks such as stemming, handling of synonyms, misspelling and so on, should be taken into consideration; if the system being developed is based on images, then examples of features can be histograms of colors, geometrical features and so on. During the literature review, we discovered that most of the projects handled the notational aspects of the expressions, that is, the real naming of the terms in a given equation and each project developed its own set of heuristics to handle the structural component.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[height=2 cm]{figures/greater_less.png}
	\caption{List of different types of grater/less than related characters in Unicode}
	\label{less_greater}
\end{figure}

@@

\section{Development with Lucene/Solr}
This section explains how the described components were implemented in the {\codefont Apache Solr/Lucene} framework.
One focus of our work was to develop a modular system that allowed easily to deploy new heuristics as they were identified.

@@

A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, more work is required. The demo setup employs the same dataset as used for experimentation.
We include an online \LaTeX editor\cite{latex_editor} that renders the input expression as the user types it.

>>>>

\section{Features Extraction}
Our main goal is to develop a system that compliments the already available search capabilities in Invenio and in particular the CDS instance. Our system was developed on top of the  the Apache Lucene/Solr framework. CDS already uses Solr as a search engine layer, so developing $5e^{x+y}$(CDS) using this technology supposed a reasonable choice. One of the main steps while building an IR tool, is understanding the data and what kind of features can be extracted from it: If the system is based on text, then tasks such as stemming, handling of synonyms, misspelling and so on, should be taken into consideration; if the system being developed is based on images, then examples of features can be histograms of colors, geometrical features and so on. During the literature review, we discovered that most of the projects handled the notational aspects of the expressions, that is, the real naming of the terms in a given equation and each project developed its own set of heuristics to handle the structural component.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[height=2 cm]{figures/greater_less.png}
	\caption{List of different types of greater/less than related characters in Unicode}
	\label{less_greater}
\end{figure}

@@

\section{Development with Lucene/Solr}
This section explains how the described components were implemented in the {\codefont Apache Lucene/Solr} framework.
One focus of our work was to develop a modular system that allowed easily to deploy new heuristics as they were identified.

@@

A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, more work is required. The demo setup employs the same dataset as used for experimentation.
We include an online \LaTeX\ editor\cite{latex_editor} that renders the input expression as the user types it.

### 2014-03-13 docs/thesis/chap-introduction.tex
proofreading fixes
Syntax and grammar fixes

Even though the main focus of CERN relies on the study of particle physics, the strong research environment has lead to important advances in several different areas, and one of the main inventions that CERN has contributed to the world is the Web. Tim Berners-Lee, in 1989, proposed a solution\cite{web_proposal} to the increasing problem of keeping track all the information related to the different experiments held at CERN, through a hypertext system.

\subsection{CDS Invenio}
CDS\cite{CDS1} (CERN Document Server) Invenio is the integrated digital library system developed and used at CERN\cite{CDS2}. To the date, it contains more than one million records and more than 400000 full-text documents. It provides tools to manage the complete workflow of a document taking care of the submission, annotation, editing, storage, searching, retrieval, displaying among other phases. Figure \ref{cds_screenshot} presents the search results for a simple query in CDS.

@@

Invenio\cite{invenio} is the software running behind CDS and is an open source project developed in parallel to CDS at CERN. Besides CDS, Invenio also supports around thirty scientific institutions worldwide including Fermilab, SLAC National Laboratory, INSPIRE and EPFL. 
Invenio is composed of several modules, each one of which can be mapped to a specific step in the workflow of a record. Figure \ref{invenio_architecture} presents the global architecture of Invenio. A detailed explanation of each module can be accessed in \cite{invenio_modules}

\begin{figure}
\centering
\includegraphics[height=10 cm]{figures/invenio.jpeg}
\label{invenio_architecture}
\caption{Invenio global architecture}
\end{figure}

>>>>

Even though the main focus of CERN relies on the study of particle physics, the strong research environment has lead to important advances in several different areas, and one of the main inventions that CERN has contributed to the world is the Web. Tim Berners-Lee, in 1989, proposed a solution\cite{web_proposal} to the increasing problem of keeping track of all the information related to the different experiments held at CERN, through a hypertext system.

\subsection{CDS & Invenio}
CDS\cite{CDS1} (CERN Document Server) is the institutional digital library system developed and used at CERN\cite{CDS2}. To this date, it contains more than one million records and more than 400000 full-text documents. It provides tools to manage the complete workflow of a document taking care of the submission, annotation, editing, storage, searching, retrieval and displaying, among other phases. Figure \ref{cds_screenshot} presents the search results for a simple query in CDS.

@@

Invenio\cite{invenio} is the open-source digital library software platform running behind CDS and it is a project developed in parallel to CDS at CERN. Besides CDS, Invenio also supports around thirty scientific institutions worldwide including Fermilab, SLAC National Laboratory, INSPIRE and EPFL. 
Invenio is composed of several modules, each one of which can be mapped to a specific step in the workflow of a record. Figure 1.2 presents the global architecture of Invenio. A detailed explanation of each module can be accessed in \cite{invenio_modules}

\begin{figure}
\centering
\includegraphics[height=15 cm]{figures/invenio.jpeg}
\label{invenio_architecture}
\caption{Invenio global architecture}
\end{figure}
